Performance of prediction models for opportunities for improvment in trauma care across patient cohorts

### 2023-12-13 manuscript.Rmd

---
title: "Performance of prediction models for opportunities for improvment in trauma care across patient cohorts"
author: "Anna Thoss"
output:
  pdf_document: default
  html_document: default
bibliography: bibliography.bib
csl: vancouver.csl
---

>>>>

---
title: "Performance of prediction models for opportunities for improvment in trauma care across patient cohorts"
author: "Anna Thoss"
output:
  pdf_document: default
  html_document: default
  word_document: default
bibliography: bibliography.bib
csl: vancouver.csl
---
